---
title: "stream.air.temp.mods.CORR_1Feb24"
author: "Carolyn Cummins"
date: "2024-02-01"
output: html_document
---

```{r}

library(lubridate)

```


Getting an updated average daily temps file for mar-apr including 2 more days in april
```{r}

cs01.daily.temps <- read.csv("cs01_daily_airtemp.csv")
cs01.daily.temps <- cs01.daily.temps %>% mutate(date=make_date(YEAR,MONTH,DAY))
str(cs01.daily.temps)

```
Get "ave.daily.temps" but in R!
Exclude 4/5 and 4/6 from the data to use to make the regressions, because we realized those data are messed up.
Make the march-april dataframe based on the original df in R instead of by hand. INCLUDE april 5 and 6 so we can model those temps instead.
```{r}

ave.air.temps.marapr<-read.csv("ave.daily.temps.mar.apr.csv")

ave.daily.temps.sept_march <- cs01.daily.temps %>% filter(date>"2017-09-20" & date<"2018-03-09")
ave.daily.temps.apr.oct <- cs01.daily.temps %>% filter(date>"2018-04-06" & date<"2018-09-29")
ave.air.temps.marapr <- cs01.daily.temps %>% filter(date>"2018-03-08" & date<"2018-04-07")
ave.air.temps <- bind_rows(ave.daily.temps.sept_march,ave.daily.temps.apr.oct)
colnames(ave.air.temps)[colnames(ave.air.temps)=="date"] <- "Group.1"


```


Watershed 1
```{r}

ws.1<-read.csv("WS1_thrumarch_apr-oct_2018.csv", header=T)
colnames(ws.1)[colnames(ws.1)=="X"] <- "date.time"
colnames(ws.1)[colnames(ws.1)=="X.1"] <- "temp.celsius"
ws.1 <- ws.1[2:33048,]
ws.1<- ws.1 %>% mutate(date=mdy_hm(date.time))
ws.1$date <- as.Date(ws.1$date)
ws.1$temp.celsius <- as.numeric(as.character(ws.1$temp.celsius))
ws.1.dailies <- aggregate(ws.1$temp.celsius,by=list(ws.1$date),FUN=mean,na.rm=T)
colnames(ws.1.dailies)[colnames(ws.1.dailies)=="x"] <- "daily.mean.temp"
ws.1.dailies <- ws.1.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

merged.ws1 <- merge(ws.1.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws1)[colnames(merged.ws1)=="TAVG"] <- "t.avg.air"
colnames(merged.ws1)[colnames(merged.ws1)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws1<-lm(t.avg.stream~t.avg.air, data=merged.ws1)
summary(mod.ws1)

#OLD#
#Watershed1 slope = 0.50799, intercept = 5.41235
#R^2=0.88

#NEW# - 24 Feb 2024
#Watershed1 slope = 0.512813, intercept=5.288590
#R^2=0.91

modeled.temps.ws1<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws1)[colnames(modeled.temps.ws1)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws1)[colnames(modeled.temps.ws1)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws1$avg.stream.temp<-(((modeled.temps.ws1$avg.air.temp)*(0.512813))+5.288590)

ws.1.marchapril.average<-mean(modeled.temps.ws1$avg.stream.temp)
ws.1.marchapril.average
#Old = 10.03
#New = 9.92

```


WS02
```{r}

ws.2<-read.csv("WS2_thrumarch_apr-oct_2018.csv", header=T)
colnames(ws.2)[colnames(ws.2)=="Date.Time..GMT.04.00"] <- "date.time"
colnames(ws.2)[colnames(ws.2)=="temp.C"] <- "temp.celsius"
ws.2 <- ws.2 %>% mutate(date=mdy_hm(date.time))
ws.2$date <- as.Date(ws.2$date)
ws.2$temp.celsius <- as.numeric(as.character(ws.2$temp.celsius))
ws.2.dailies <- aggregate(ws.2$temp.celsius,by=list(ws.2$date),FUN=mean,na.rm=T)
colnames(ws.2.dailies)[colnames(ws.2.dailies)=="x"] <- "daily.mean.temp"
ws.2.dailies <- ws.2.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

merged.ws2<-merge(ws.2.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws2)[colnames(merged.ws2)=="TAVG"] <- "t.avg.air"
colnames(merged.ws2)[colnames(merged.ws2)=="daily.mean.temp"] <- "t.avg.stream"


mod.ws2<-lm(t.avg.stream~t.avg.air, data=merged.ws2)
summary(mod.ws2)
#OLD#
#WS2 slope = 0.4432, intercept=7.0962
#R^2=0.86

#NEW#
#slope = 0.447578, intercept=6.983286 R^2 = 0.89

modeled.temps.ws2<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws2)[colnames(modeled.temps.ws2)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws2)[colnames(modeled.temps.ws2)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws2$avg.stream.temp<-(((modeled.temps.ws2$avg.air.temp)*(0.447578))+6.983286)

ws.2.marchapril.average<-mean(modeled.temps.ws2$avg.stream.temp)
ws.2.marchapril.average
#11.03
#OLD = 11.13

```

Watershed 6
```{r}

ws.6<-read.csv("WS6_thrumarch_apr-oct_2018.csv", header=T)
colnames(ws.6)[colnames(ws.6)=="Date.Time..GMT.04.00"] <- "date.time"
ws.6 <- ws.6 %>% mutate(date=mdy_hm(date.time))
ws.6$date <- as.Date(ws.6$date)
ws.6$temp.celsius <- as.numeric(as.character(ws.6$temp.celsius))
ws.6.dailies <- aggregate(ws.6$temp.celsius,by=list(ws.6$date),FUN=mean,na.rm=T)
colnames(ws.6.dailies)[colnames(ws.6.dailies)=="x"] <- "daily.mean.temp"
ws.6.dailies <- ws.6.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))


merged.ws6<-merge(ws.6.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws6)[colnames(merged.ws6)=="TAVG"] <- "t.avg.air"
colnames(merged.ws6)[colnames(merged.ws6)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws6<-lm(t.avg.stream~t.avg.air, data=merged.ws6)
summary(mod.ws6)
#OLD#
#WS6 slope = 0.65862, intercept=3.44360
#R^2=0.88

#NEW#
#slope=0.66392, intercept=3.30743

modeled.temps.ws6<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws6)[colnames(modeled.temps.ws6)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws6)[colnames(modeled.temps.ws6)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws6$avg.stream.temp<-(((modeled.temps.ws6$avg.air.temp)*(0.66392))+3.30743)

ws.6.marchapril.average<-mean(modeled.temps.ws6$avg.stream.temp)
ws.6.marchapril.average
#9.31 (old = 9.43)

```


Watershed 7
```{r}

ws.7<-read.csv("WS7_thrumarch_apr-oct_2018.csv", header=T)
ws.7 <- ws.7 %>% mutate(Date=mdy_hm(date.time))
ws.7$Date <- as.Date(ws.7$Date)
ws.7$temp.celsius <- as.numeric(as.character(ws.7$temp.celsius))
ws.7$Date <- as.factor(ws.7$Date)
ws.7.dailies <- aggregate(ws.7$temp.celsius,by=list(ws.7$Date),FUN=mean,na.rm=T)
colnames(ws.7.dailies)[colnames(ws.7.dailies)=="x"] <- "daily.mean.temp"
ws.7.dailies <- ws.7.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

merged.ws7<-merge(ws.7.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws7)[colnames(merged.ws7)=="TAVG"] <- "t.avg.air"
colnames(merged.ws7)[colnames(merged.ws7)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws7<-lm(t.avg.stream~t.avg.air, data=merged.ws7)
summary(mod.ws7)
#OLD#
#WS7 slope = 0.477799 intercept=6.164554
#R^2=0.88

#NEW
#slope=0.482476, intercept=6.044461


modeled.temps.ws7<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws7)[colnames(modeled.temps.ws7)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws7)[colnames(modeled.temps.ws7)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws7$avg.stream.temp<-(((modeled.temps.ws7$avg.air.temp)*(0.482476))+6.044461)

ws.7.marchapril.average<-mean(modeled.temps.ws7$avg.stream.temp)
ws.7.marchapril.average
#10.40574 (old = 10.51039)

```

WS13
```{r}

ws.13<-read.csv("WS13_thrumarch_apr-oct_2018.csv", header=T)
ws.13 <- ws.13 %>% mutate(Date=mdy_hm(date.time))
ws.13$Date <- as.Date(ws.13$Date)
ws.13$temp.celsius <- as.numeric(as.character(ws.13$temp.celsius))
ws.13$Date <- as.factor(ws.13$Date)
ws.13.dailies <- aggregate(ws.13$temp.celsius,by=list(ws.13$Date),FUN=mean,na.rm=T)
colnames(ws.13.dailies)[colnames(ws.13.dailies)=="x"] <- "daily.mean.temp"
ws.13.dailies <- ws.13.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))


merged.ws13 <- merge(ws.13.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws13)[colnames(merged.ws13)=="TAVG"] <- "t.avg.air"
colnames(merged.ws13)[colnames(merged.ws13)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws13<-lm(t.avg.stream~t.avg.air, data=merged.ws13)
summary(mod.ws13)
#OLD#
#WS13 slope = 0.5326 intercept=5.1208
#R^2=0.87
#NEW#
#slope=0.537657, intercept=4.990231

modeled.temps.ws13<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws13)[colnames(modeled.temps.ws13)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws13)[colnames(modeled.temps.ws13)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws13$avg.stream.temp<-(((modeled.temps.ws13$avg.air.temp)*(0.537657))+4.990231)

ws.13.marchapril.average<-mean(modeled.temps.ws13$avg.stream.temp)
ws.13.marchapril.average
#9.85031 (old=9.965076)

```


Watershed 14
```{r}

ws.14<-read.csv("WS14_thrumarch_apr-oct_2018.csv", header=T)
ws.14 <- ws.14 %>% mutate(Date=mdy_hm(date.time))
ws.14$Date <- as.Date(ws.14$Date)
ws.14$temp.celsius <- as.numeric(as.character(ws.14$temp.celsius))
ws.14$Date <- as.factor(ws.14$Date)
ws.14.dailies <- aggregate(ws.14$temp.celsius,by=list(ws.14$Date),FUN=mean,na.rm=T)
colnames(ws.14.dailies)[colnames(ws.14.dailies)=="x"] <- "daily.mean.temp"
ws.14.dailies <- ws.14.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

merged.ws14<-merge(ws.14.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws14)[colnames(merged.ws14)=="TAVG"] <- "t.avg.air"
colnames(merged.ws14)[colnames(merged.ws14)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws14<-lm(t.avg.stream~t.avg.air, data=merged.ws14)
summary(mod.ws14)
#OLD#
#WS14 slope = 0.59332 intercept=4.17439
#R^2=0.88

#NEW#
#slope=0.59849, intercept=4.04151


modeled.temps.ws14<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws14)[colnames(modeled.temps.ws14)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws14)[colnames(modeled.temps.ws14)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws14$avg.stream.temp<-(((modeled.temps.ws14$avg.air.temp)*(0.59849))+4.04151)

ws.14.marchapril.average<-mean(modeled.temps.ws14$avg.stream.temp)
ws.14.marchapril.average
#9.451481 (old=9.570947)

```


```{r}

ws.18<-read.csv("WS18_thrumarch_apr-oct_2018.csv", header=T)
ws.18 <- ws.18 %>% mutate(Date=mdy_hm(date.time))
ws.18$Date <- as.Date(ws.18$Date)
ws.18$temp.celsius <- as.numeric(as.character(ws.18$temp.celsius))
ws.18$Date <- as.factor(ws.18$Date)
ws.18.dailies <- aggregate(ws.18$temp.celsius,by=list(ws.18$Date),FUN=mean,na.rm=T)
colnames(ws.18.dailies)[colnames(ws.18.dailies)=="x"] <- "daily.mean.temp"
ws.18.dailies <- ws.18.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

merged.ws18<-merge(ws.18.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws18)[colnames(merged.ws18)=="TAVG"] <- "t.avg.air"
colnames(merged.ws18)[colnames(merged.ws18)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws18<-lm(t.avg.stream~t.avg.air, data=merged.ws18)
summary(mod.ws18)
#OLD
#WS18 slope = 0.57982 intercept=4.35862
#R^2=0.87

#NEW#
#slope:0.58503, intercept=4.22477


modeled.temps.ws18<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws18)[colnames(modeled.temps.ws18)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws18)[colnames(modeled.temps.ws18)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws18$avg.stream.temp<-(((modeled.temps.ws18$avg.air.temp)*(0.58503))+4.22477)

ws.18.marchapril.average<-mean(modeled.temps.ws18$avg.stream.temp)
ws.18.marchapril.average
#9.513071 (old=9.632387)

```


Watershed 27
```{r}

ws.27<-read.csv("WS27_thrumarch_apr-oct_2018.csv", header=T)
ws.27 <- ws.27 %>% mutate(Date=mdy_hm(date.time))
ws.27$Date <- as.Date(ws.27$Date)
ws.27$temp.celsius <- as.numeric(as.character(ws.27$temp.celsius))
ws.27$Date <- as.factor(ws.27$Date)
ws.27.dailies <- aggregate(ws.27$temp.celsius,by=list(ws.27$Date),FUN=mean,na.rm=T)
colnames(ws.27.dailies)[colnames(ws.27.dailies)=="x"] <- "daily.mean.temp"
ws.27.dailies <- ws.27.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

merged.ws27<-merge(ws.27.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws27)[colnames(merged.ws27)=="TAVG"] <- "t.avg.air"
colnames(merged.ws27)[colnames(merged.ws27)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws27<-lm(t.avg.stream~t.avg.air, data=merged.ws27)
summary(mod.ws27)
#OLD#
#WS27 slope = 0.53149 intercept=3.89423
#R^2=0.83

#NEW#
#slope=0.53684, intercept=3.75678

modeled.temps.ws27<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws27)[colnames(modeled.temps.ws27)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws27)[colnames(modeled.temps.ws27)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws27$avg.stream.temp<-(((modeled.temps.ws27$avg.air.temp)*(0.53684))+3.75678)

ws.27.marchapril.average<-mean(modeled.temps.ws27$avg.stream.temp)
ws.27.marchapril.average
#8.609474 (old = 8.72841)

```

Watershed 31
```{r}

ws.31<-read.csv("WS31_thrumarch_apr-oct_2018.csv", header=T)
ws.31 <- ws.31 %>% mutate(Date=mdy_hm(date.time))
ws.31$Date <- as.Date(ws.31$Date)
ws.31$temp.celsius <- as.numeric(as.character(ws.31$temp.celsius))
ws.31$Date <- as.factor(ws.31$Date)
ws.31.dailies <- aggregate(ws.31$temp.celsius,by=list(ws.31$Date),FUN=mean,na.rm=T)
colnames(ws.31.dailies)[colnames(ws.31.dailies)=="x"] <- "daily.mean.temp"
ws.31.dailies <- ws.31.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

merged.ws31<-merge(ws.31.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws31)[colnames(merged.ws31)=="TAVG"] <- "t.avg.air"
colnames(merged.ws31)[colnames(merged.ws31)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws31<-lm(t.avg.stream~t.avg.air, data=merged.ws31)
summary(mod.ws31)
#OLD#
#WS31 slope = 0.439256 intercept=6.52829
#R^2=0.88

#NEW#
#slope=0.443858, intercept=6.410182

modeled.temps.ws31<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws31)[colnames(modeled.temps.ws31)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws31)[colnames(modeled.temps.ws31)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws31$avg.stream.temp<-(((modeled.temps.ws31$avg.air.temp)*(0.443858))+6.410182)

ws.31.marchapril.average<-mean(modeled.temps.ws31$avg.stream.temp)
ws.31.marchapril.average
#10.42238 (old=10.52355)

```


Watershed 32
```{r}

ws.32<-read.csv("WS32_thrumarch_apr-oct_2018.csv", header=T)
ws.32 <- ws.32 %>% mutate(Date=mdy_hm(date.time))
ws.32$Date <- as.Date(ws.32$Date)
ws.32$temp.celsius <- as.numeric(as.character(ws.32$temp.celsius))
ws.32$Date <- as.factor(ws.32$Date)
ws.32.dailies <- aggregate(ws.32$temp.celsius,by=list(ws.32$Date),FUN=mean,na.rm=T)
ws.32.dailies <- ws.32.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

colnames(ws.32.dailies)[colnames(ws.32.dailies)=="x"] <- "daily.mean.temp"
merged.ws32<-merge(ws.32.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws32)[colnames(merged.ws32)=="TAVG"] <- "t.avg.air"
colnames(merged.ws32)[colnames(merged.ws32)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws32<-lm(t.avg.stream~t.avg.air, data=merged.ws32)
summary(mod.ws32)
#OLD#
#WS32 slope = 0.477192 intercept=5.513446
#R^2=0.87

#NEW#
#slope=0.482009, intercept=5.389803

modeled.temps.ws32<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws32)[colnames(modeled.temps.ws32)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws32)[colnames(modeled.temps.ws32)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws32$avg.stream.temp<-(((modeled.temps.ws32$avg.air.temp)*(0.482009))+5.389803)

ws.32.marchapril.average<-mean(modeled.temps.ws32$avg.stream.temp)
ws.32.marchapril.average
#9.74686 (old=9.853758)

```


Watershed 36
```{r}

ws.36<-read.csv("WS36_thrumarch_apr-oct_2018.csv", header=T)
ws.36 <- ws.36 %>% mutate(Date=mdy_hm(date.time))
ws.36$Date <- as.Date(ws.36$Date)
ws.36$temp.celsius <- as.numeric(as.character(ws.36$temp.celsius))
ws.36$Date <- as.factor(ws.36$Date)
ws.36.dailies <- aggregate(ws.36$temp.celsius,by=list(ws.36$Date),FUN=mean,na.rm=T)
colnames(ws.36.dailies)[colnames(ws.36.dailies)=="x"] <- "daily.mean.temp"
ws.36.dailies <- ws.36.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

merged.ws36<-merge(ws.36.dailies,ave.air.temps,by="Group.1")
colnames(merged.ws36)[colnames(merged.ws36)=="TAVG"] <- "t.avg.air"
colnames(merged.ws36)[colnames(merged.ws36)=="daily.mean.temp"] <- "t.avg.stream"

mod.ws36<-lm(t.avg.stream~t.avg.air, data=merged.ws36)
summary(mod.ws36)
#OLD#
#WS36 slope = 0.45853 intercept=5.59441
#R^2=0.85

#NEW
#slope=0.463312, intercept=5.471762

modeled.temps.ws36<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.ws36)[colnames(modeled.temps.ws36)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.ws36)[colnames(modeled.temps.ws36)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.ws36$avg.stream.temp<-(((modeled.temps.ws36$avg.air.temp)*(0.463312))+5.471762)

ws.36.marchapril.average<-mean(modeled.temps.ws36$avg.stream.temp)
ws.36.marchapril.average
#9.65981 (old=9.764981)

```

WSLSF (WS08)
```{r}

ws.LSF<-read.csv("WSLSF_thrumarch_apr-oct_2018.csv", header=T)
ws.LSF <- ws.LSF %>% mutate(Date=mdy_hm(date.time))
ws.LSF$Date <- as.Date(ws.LSF$Date)
ws.LSF$temp.celsius <- as.numeric(as.character(ws.LSF$temp.celsius))
ws.LSF$Date <- as.factor(ws.LSF$Date)
ws.LSF.dailies <- aggregate(ws.LSF$temp.celsius,by=list(ws.LSF$Date),FUN=mean,na.rm=T)
colnames(ws.LSF.dailies)[colnames(ws.LSF.dailies)=="x"] <- "daily.mean.temp"
ws.LSF.dailies <- ws.LSF.dailies %>% filter(!(Group.1 %in% as.Date(c("2018-04-05", "2018-04-06"))))

merged.wsLSF<-merge(ws.LSF.dailies,ave.air.temps,by="Group.1")
colnames(merged.wsLSF)[colnames(merged.wsLSF)=="TAVG"] <- "t.avg.air"
colnames(merged.wsLSF)[colnames(merged.wsLSF)=="daily.mean.temp"] <- "t.avg.stream"

mod.wsLSF<-lm(t.avg.stream~t.avg.air, data=merged.wsLSF)
summary(mod.wsLSF)
#OLD#
#WSLSF slope = 0.56573 intercept=4.52781
#R^2=0.89

#NEW#
#slope=0.570750, intercept=4.393469

modeled.temps.wsLSF<-data.frame(ave.air.temps.marapr$date, ave.air.temps.marapr$TAVG)
colnames(modeled.temps.wsLSF)[colnames(modeled.temps.wsLSF)=="ave.air.temps.marapr.TAVG"] <- "avg.air.temp"
colnames(modeled.temps.wsLSF)[colnames(modeled.temps.wsLSF)=="ave.air.temps.marapr.date"] <- "date"
modeled.temps.wsLSF$avg.stream.temp<-(((modeled.temps.wsLSF$avg.air.temp)*(0.570750))+4.393469)

ws.LSF.marchapril.average<-mean(modeled.temps.wsLSF$avg.stream.temp)
ws.LSF.marchapril.average
#9.552688 (old=9.673421)

```


############
31 March 2022 -- need to model 8/31/18-9/28/18 for LSF
1 Feb 24 - update with new regression
```{r}

#1.0 - get air temps for this period from CS01
ave.air.temps.augsep <- ave.air.temps[c(318:346),]
modeled.temps.wsLSF.augsep <- data.frame(ave.air.temps.augsep$Group.1, ave.air.temps.augsep$TAVG)
colnames(modeled.temps.wsLSF.augsep)[colnames(modeled.temps.wsLSF.augsep)=="ave.air.temps.augsep.Group.1"] <- "date"
colnames(modeled.temps.wsLSF.augsep)[colnames(modeled.temps.wsLSF.augsep)=="ave.air.temps.augsep.TAVG"] <- "avg.air.temp"
modeled.temps.wsLSF.augsep$avg.stream.temp <- (((modeled.temps.wsLSF.augsep$avg.air.temp)*(0.570750))+4.393469)

wsLSF.augsep.dailies <- data.frame("date"=modeled.temps.wsLSF.augsep$date, "temp.celsius"=modeled.temps.wsLSF.augsep$avg.stream.temp)
wsLSF.augsep.dailies$stream <- "WS08"
write.csv(wsLSF.augsep.dailies, "WS08_dailies_31Aug-29Sep_2018_1Feb24.csv")
############

```



######################################################################################################
making new dataframes with just date and mean temp for all the streams for the modeled data from march-april of 2018
```{r}

#WS1
ws.1.marapr.dailies<-data.frame("date" = modeled.temps.ws1$date, "temp.celsius"=modeled.temps.ws1$avg.stream.temp)
colnames(ws.1.marapr.dailies)[colnames(ws.1.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.1.marapr.dailies)[colnames(ws.1.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.1.marapr.dailies$stream<-"WS01"

#WS2
ws.2.marapr.dailies<-data.frame("date" = modeled.temps.ws2$date, "temp.celsius"=modeled.temps.ws2$avg.stream.temp)
colnames(ws.2.marapr.dailies)[colnames(ws.2.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.2.marapr.dailies)[colnames(ws.2.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.2.marapr.dailies$stream<-"WS02"

#WS6
ws.6.marapr.dailies<-data.frame("date" = modeled.temps.ws6$date, "temp.celsius"=modeled.temps.ws6$avg.stream.temp)
colnames(ws.6.marapr.dailies)[colnames(ws.6.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.6.marapr.dailies)[colnames(ws.6.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.6.marapr.dailies$stream<-"WS06"

#WS7
ws.7.marapr.dailies<-data.frame("date" = modeled.temps.ws7$date, "temp.celsius"=modeled.temps.ws7$avg.stream.temp)
colnames(ws.7.marapr.dailies)[colnames(ws.7.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.7.marapr.dailies)[colnames(ws.7.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.7.marapr.dailies$stream<-"WS07"

#WS13
ws.13.marapr.dailies<-data.frame("date" = modeled.temps.ws13$date, "temp.celsius"=modeled.temps.ws13$avg.stream.temp)
colnames(ws.13.marapr.dailies)[colnames(ws.13.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.13.marapr.dailies)[colnames(ws.13.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.13.marapr.dailies$stream<-"WS13"

#WS14
ws.14.marapr.dailies<-data.frame("date" = modeled.temps.ws14$date, "temp.celsius"=modeled.temps.ws14$avg.stream.temp)
colnames(ws.14.marapr.dailies)[colnames(ws.14.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.14.marapr.dailies)[colnames(ws.14.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.14.marapr.dailies$stream<-"WS14"

#WS18
ws.18.marapr.dailies<-data.frame("date" = modeled.temps.ws18$date, "temp.celsius"=modeled.temps.ws18$avg.stream.temp)
colnames(ws.18.marapr.dailies)[colnames(ws.18.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.18.marapr.dailies)[colnames(ws.18.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.18.marapr.dailies$stream<-"WS18"

#WS27
ws.27.marapr.dailies<-data.frame("date" = modeled.temps.ws27$date, "temp.celsius"=modeled.temps.ws27$avg.stream.temp)
colnames(ws.27.marapr.dailies)[colnames(ws.27.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.27.marapr.dailies)[colnames(ws.27.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.27.marapr.dailies$stream<-"WS27"

#WS31
ws.31.marapr.dailies<-data.frame("date" = modeled.temps.ws31$date, "temp.celsius"=modeled.temps.ws31$avg.stream.temp)
colnames(ws.31.marapr.dailies)[colnames(ws.31.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.31.marapr.dailies)[colnames(ws.31.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.31.marapr.dailies$stream<-"WS31"

#WS32
ws.32.marapr.dailies<-data.frame("date" = modeled.temps.ws32$date, "temp.celsius"=modeled.temps.ws32$avg.stream.temp)
colnames(ws.32.marapr.dailies)[colnames(ws.32.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.32.marapr.dailies)[colnames(ws.32.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.32.marapr.dailies$stream<-"WS32"

#WS36
ws.36.marapr.dailies<-data.frame("date" = modeled.temps.ws36$date, "temp.celsius"=modeled.temps.ws36$avg.stream.temp)
colnames(ws.36.marapr.dailies)[colnames(ws.36.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.36.marapr.dailies)[colnames(ws.36.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.36.marapr.dailies$stream<-"WS36"

#WSLSF
ws.LSF.marapr.dailies<-data.frame("date" = modeled.temps.wsLSF$date, "temp.celsius"=modeled.temps.wsLSF$avg.stream.temp)
colnames(ws.LSF.marapr.dailies)[colnames(ws.LSF.marapr.dailies)=="date"] <- "Group.1"
colnames(ws.LSF.marapr.dailies)[colnames(ws.LSF.marapr.dailies)=="temp.celsius"] <- "daily.mean.temp"
ws.LSF.marapr.dailies$stream<-"WS08"

```


#one big dataframe with all the modeled data
```{r}

all.modeled.data<-data.frame(bind_rows(ws.1.marapr.dailies, ws.2.marapr.dailies, ws.6.marapr.dailies, ws.7.marapr.dailies,
          ws.13.marapr.dailies, ws.14.marapr.dailies, ws.18.marapr.dailies, ws.27.marapr.dailies,
          ws.31.marapr.dailies, ws.32.marapr.dailies, ws.36.marapr.dailies, ws.LSF.marapr.dailies))

colnames(all.modeled.data)[colnames(all.modeled.data)=="Group.1"] <- "date"
colnames(all.modeled.data)[colnames(all.modeled.data)=="daily.mean.temp"] <- "temp.celsius"


write.csv(all.modeled.data, "all.modeled.data.1Feb24.csv")

```



