---
title: "SI_Phys_Chem_LitterBreakdown_Master_File"
author: "Carolyn Cummins"
date: "10/3/2023"
output: html_document
---
This is an Rmd file for reading in all the serial incubations data - temperature, discharge, nutrients, and litter breakdown - and getting it into one dataframe for analysis.

***UPDATED 10 October 2023 for manuscript revision. In this version, the litter breakdown data that we read in has been filtered to exclude weight "gains" (1 observation in entire dataset) and, as a consequence of that filtering, also all the NA/Inf values

****Updated 1 Feb 2024 with corrected, modeled values for April 5 and 6 for all streams

Load packages
```{r}
library(tidyverse)
library(lubridate)
library(Rmisc)
library(lme4)
library(lmerTest)
library(ggplot2)
```


Read in the data
```{r}

#litter breakdown
lb_si_yr1 <- read.csv("litter_breakdown_coarse_fine_yr1_all.3Oct23.csv")
lb_si_yr1 <- lb_si_yr1 %>% mutate(date_coll=ymd(date_coll))
lb_si_yr1 <- lb_si_yr1 %>% mutate(date_dep=ymd(date_dep))


lb_si_yr2 <- read.csv("litter_breakdown_coarse_fine_yr2_all.4Mar23.csv")
lb_si_yr2 <- lb_si_yr2 %>% mutate(date_coll=ymd(date_coll))
lb_si_yr2 <- lb_si_yr2 %>% mutate(date_dep=ymd(date_dep))

#temp
dep_temp_si_yr1 <-read.csv("landscape_deployment_temp_masterlong_SIyr1.1Feb24.csv")
dep_temp_si_yr1 <- dep_temp_si_yr1 %>% mutate(start_date=ymd(start_date))
dep_temp_si_yr1 <- dep_temp_si_yr1 %>% mutate(end_date=ymd(end_date))
colnames(dep_temp_si_yr1)[colnames(dep_temp_si_yr1)=="start_date"] <- "date_dep"
colnames(dep_temp_si_yr1)[colnames(dep_temp_si_yr1)=="end_date"] <- "date_coll"
colnames(dep_temp_si_yr1)[colnames(dep_temp_si_yr1)=="days_in_record"] <- "days_in_record_temp"

dep_temp_si_yr2 <- read.csv("landscape_deployment_temp_masterlong_SIyr2_UPD23Feb23.csv")
dep_temp_si_yr2 <- dep_temp_si_yr2 %>% mutate(start_date=ymd(start_date))
dep_temp_si_yr2 <- dep_temp_si_yr2 %>% mutate(end_date=ymd(end_date))
colnames(dep_temp_si_yr2)[colnames(dep_temp_si_yr2)=="start_date"] <- "date_dep"
colnames(dep_temp_si_yr2)[colnames(dep_temp_si_yr2)=="end_date"] <- "date_coll"
colnames(dep_temp_si_yr2)[colnames(dep_temp_si_yr2)=="days_in_record"] <- "days_in_record_temp"

#discharge
dep_discharge_si_yr1 <- read.csv("landscape_deployment_discharge_masterlong_SIyr1_UPD23Feb23.csv")
dep_discharge_si_yr1 <- dep_discharge_si_yr1 %>% mutate(start_date=ymd(start_date))
dep_discharge_si_yr1 <- dep_discharge_si_yr1 %>% mutate(end_date=ymd(end_date))
colnames(dep_discharge_si_yr1)[colnames(dep_discharge_si_yr1)=="start_date"] <- "date_dep"
colnames(dep_discharge_si_yr1)[colnames(dep_discharge_si_yr1)=="end_date"] <- "date_coll"

dep_discharge_si_yr2 <- read.csv("landscape_deployment_discharge_masterlong_SIyr2_UPD23Feb23.csv")
dep_discharge_si_yr2 <- dep_discharge_si_yr2 %>% mutate(start_date=ymd(start_date))
dep_discharge_si_yr2 <- dep_discharge_si_yr2 %>% mutate(end_date=ymd(end_date))
colnames(dep_discharge_si_yr2)[colnames(dep_discharge_si_yr2)=="start_date"] <- "date_dep"
colnames(dep_discharge_si_yr2)[colnames(dep_discharge_si_yr2)=="end_date"] <- "date_coll"

#nutrients
dep_nutrients_si_yr1 <- read.csv("deployment_nuts_masterlong_SIyr1.csv")
dep_nutrients_si_yr1 <- dep_nutrients_si_yr1 %>% mutate(start_date=ymd(start_date))
dep_nutrients_si_yr1 <- dep_nutrients_si_yr1 %>% mutate(end_date=ymd(end_date))
colnames(dep_nutrients_si_yr1)[colnames(dep_nutrients_si_yr1)=="start_date"] <- "date_dep"
colnames(dep_nutrients_si_yr1)[colnames(dep_nutrients_si_yr1)=="end_date"] <- "date_coll"

dep_nutrients_si_yr2 <- read.csv("deployment_nuts_masterlong_SIyr2_UPD23Feb23.csv")
dep_nutrients_si_yr2 <- dep_nutrients_si_yr2 %>% mutate(start_date=ymd(start_date))
dep_nutrients_si_yr2 <- dep_nutrients_si_yr2 %>% mutate(end_date=ymd(end_date))
colnames(dep_nutrients_si_yr2)[colnames(dep_nutrients_si_yr2)=="start_date"] <- "date_dep"
colnames(dep_nutrients_si_yr2)[colnames(dep_nutrients_si_yr2)=="end_date"] <- "date_coll"

#deleting unnecessary streams from nutrient data yr 1 and 2 - yr1 has some yr2 streams and yr2 has some yr1 streams...
dep_nutrients_si_yr1<-subset(dep_nutrients_si_yr1, stream!="WS17" & stream!="WS34" & stream!="WS37")
dep_nutrients_si_yr2<-subset(dep_nutrients_si_yr2, stream!="WS01" & stream!="WS02" & stream!="WS06" & stream!="WS07" & stream!="WS08" & stream!="WS13" & stream!="WS14" & stream!="WS18" & stream!="WS27" & stream!="WS31" & stream!="WS32" & stream!="WS36")

#deployments
deployments_yr1 <- read.csv("SI_yr1_deployments.csv")
deployments_yr1 <- deployments_yr1 %>% mutate(date_dep=mdy(date_dep))
deployments_yr1 <- deployments_yr1 %>% mutate(date_coll=mdy(date_coll))

deployments_yr2 <- read.csv("SI_yr2_deployments_UPD23Feb23.csv")
deployments_yr2 <- deployments_yr2 %>% mutate(date_dep=mdy(date_dep))
deployments_yr2 <- deployments_yr2 %>% mutate(date_coll=mdy(date_coll))

#delete annoying first column in all the dfs
lb_si_yr1$X <- NULL
lb_si_yr2$X <- NULL
dep_discharge_si_yr1$X <- NULL
dep_discharge_si_yr2$X <- NULL
dep_nutrients_si_yr1$X <- NULL
dep_nutrients_si_yr2$X <- NULL
dep_temp_si_yr1$X <- NULL
dep_temp_si_yr2$X <- NULL

```


#Getting deployment-level litter breakdown data - YR1 and YR2, then bind the two
```{r}
#YR1
summ_k_coarse_yr1 <- summarySE(data=lb_si_yr1,measurevar="abs_val_k_coarse", groupvars=c("date_dep","date_coll", "rhodo_acer", "stream"), na.rm=TRUE)
colnames(summ_k_coarse_yr1)[colnames(summ_k_coarse_yr1)=="abs_val_k_coarse"] <- "mean_k_coarse"
colnames(summ_k_coarse_yr1)[colnames(summ_k_coarse_yr1)=="sd"] <- "sd_k_coarse"
colnames(summ_k_coarse_yr1)[colnames(summ_k_coarse_yr1)=="se"] <- "se_k_coarse"
colnames(summ_k_coarse_yr1)[colnames(summ_k_coarse_yr1)=="ci"] <- "ci_k_coarse"
colnames(summ_k_coarse_yr1)[colnames(summ_k_coarse_yr1)=="N"] <- "N_coarse"

summ_k_fine_yr1 <- summarySE(data=lb_si_yr1,measurevar="abs_val_k_fine", groupvars=c("date_dep","date_coll", "rhodo_acer", "stream"), na.rm=TRUE)
colnames(summ_k_fine_yr1)[colnames(summ_k_fine_yr1)=="abs_val_k_fine"] <- "mean_k_fine"
colnames(summ_k_fine_yr1)[colnames(summ_k_fine_yr1)=="sd"] <- "sd_k_fine"
colnames(summ_k_fine_yr1)[colnames(summ_k_fine_yr1)=="se"] <- "se_k_fine"
colnames(summ_k_fine_yr1)[colnames(summ_k_fine_yr1)=="ci"] <- "ci_k_fine"
colnames(summ_k_fine_yr1)[colnames(summ_k_fine_yr1)=="N"] <- "N_fine"

summ_k_shred_yr1 <- summarySE(data=lb_si_yr1,measurevar="abs_val_k_shred", groupvars=c("date_dep","date_coll", "rhodo_acer", "stream"), na.rm=TRUE)
colnames(summ_k_shred_yr1)[colnames(summ_k_shred_yr1)=="abs_val_k_shred"] <- "mean_k_shred"
colnames(summ_k_shred_yr1)[colnames(summ_k_shred_yr1)=="sd"] <- "sd_k_shred"
colnames(summ_k_shred_yr1)[colnames(summ_k_shred_yr1)=="se"] <- "se_k_shred"
colnames(summ_k_shred_yr1)[colnames(summ_k_shred_yr1)=="ci"] <- "ci_k_shred"
colnames(summ_k_shred_yr1)[colnames(summ_k_shred_yr1)=="N"] <- "N_shred"

###NEW SHREDDER K (Lecerf et al. 2017)!### -- YEAR 1
summ_k_shred_new_yr1 <- summarySE(data=lb_si_yr1,measurevar="new_shredder_k", groupvars=c("date_dep","date_coll", "rhodo_acer", "stream"), na.rm=TRUE)
colnames(summ_k_shred_new_yr1)[colnames(summ_k_shred_new_yr1)=="new_shredder_k"] <- "mean_k_shred_new"
colnames(summ_k_shred_new_yr1)[colnames(summ_k_shred_new_yr1)=="sd"] <- "sd_k_shred_new"
colnames(summ_k_shred_new_yr1)[colnames(summ_k_shred_new_yr1)=="se"] <- "se_k_shred_new"
colnames(summ_k_shred_new_yr1)[colnames(summ_k_shred_new_yr1)=="ci"] <- "ci_k_shred_new"
colnames(summ_k_shred_new_yr1)[colnames(summ_k_shred_new_yr1)=="N"] <- "N_shred_new"

mergecf1 <- merge(summ_k_coarse_yr1, summ_k_fine_yr1, by=c("date_dep", "date_coll", "rhodo_acer", "stream"))
mergecfs1 <- merge(mergecf1, summ_k_shred_yr1, by=c("date_dep","date_coll", "rhodo_acer", "stream"))
mergecfss1 <- merge(mergecfs1, summ_k_shred_new_yr1, by=c("date_dep","date_coll", "rhodo_acer", "stream"))
lb_si_yr1_dep <- merge(mergecfss1, deployments_yr1, by=c("date_dep", "date_coll"))

#YR2
summ_k_coarse_yr2 <- summarySE(data=lb_si_yr2,measurevar="abs_val_k_coarse", groupvars=c("date_dep","date_coll", "rhodo_acer", "stream"), na.rm=TRUE)
colnames(summ_k_coarse_yr2)[colnames(summ_k_coarse_yr2)=="abs_val_k_coarse"] <- "mean_k_coarse"
colnames(summ_k_coarse_yr2)[colnames(summ_k_coarse_yr2)=="sd"] <- "sd_k_coarse"
colnames(summ_k_coarse_yr2)[colnames(summ_k_coarse_yr2)=="se"] <- "se_k_coarse"
colnames(summ_k_coarse_yr2)[colnames(summ_k_coarse_yr2)=="ci"] <- "ci_k_coarse"
colnames(summ_k_coarse_yr2)[colnames(summ_k_coarse_yr2)=="N"] <- "N_coarse"

summ_k_fine_yr2 <- summarySE(data=lb_si_yr2,measurevar="abs_val_k_fine", groupvars=c("date_dep","date_coll", "rhodo_acer", "stream"), na.rm=TRUE)
colnames(summ_k_fine_yr2)[colnames(summ_k_fine_yr2)=="abs_val_k_fine"] <- "mean_k_fine"
colnames(summ_k_fine_yr2)[colnames(summ_k_fine_yr2)=="sd"] <- "sd_k_fine"
colnames(summ_k_fine_yr2)[colnames(summ_k_fine_yr2)=="se"] <- "se_k_fine"
colnames(summ_k_fine_yr2)[colnames(summ_k_fine_yr2)=="ci"] <- "ci_k_fine"
colnames(summ_k_fine_yr2)[colnames(summ_k_fine_yr2)=="N"] <- "N_fine"

summ_k_shred_yr2 <- summarySE(data=lb_si_yr2,measurevar="abs_val_k_shred", groupvars=c("date_dep","date_coll", "rhodo_acer", "stream"), na.rm=TRUE)
colnames(summ_k_shred_yr2)[colnames(summ_k_shred_yr2)=="abs_val_k_shred"] <- "mean_k_shred"
colnames(summ_k_shred_yr2)[colnames(summ_k_shred_yr2)=="sd"] <- "sd_k_shred"
colnames(summ_k_shred_yr2)[colnames(summ_k_shred_yr2)=="se"] <- "se_k_shred"
colnames(summ_k_shred_yr2)[colnames(summ_k_shred_yr2)=="ci"] <- "ci_k_shred"
colnames(summ_k_shred_yr2)[colnames(summ_k_shred_yr2)=="N"] <- "N_shred"

###NEW SHREDDER K (Lecerf et al. 2017)!### -- YEAR 2
summ_k_shred_new_yr2 <- summarySE(data=lb_si_yr2,measurevar="new_shredder_k", groupvars=c("date_dep","date_coll", "rhodo_acer", "stream"), na.rm=TRUE)
colnames(summ_k_shred_new_yr2)[colnames(summ_k_shred_new_yr2)=="new_shredder_k"] <- "mean_k_shred_new"
colnames(summ_k_shred_new_yr2)[colnames(summ_k_shred_new_yr2)=="sd"] <- "sd_k_shred_new"
colnames(summ_k_shred_new_yr2)[colnames(summ_k_shred_new_yr2)=="se"] <- "se_k_shred_new"
colnames(summ_k_shred_new_yr2)[colnames(summ_k_shred_new_yr2)=="ci"] <- "ci_k_shred_new"
colnames(summ_k_shred_new_yr2)[colnames(summ_k_shred_new_yr2)=="N"] <- "N_shred_new"

mergecf2 <- merge(summ_k_coarse_yr2, summ_k_fine_yr2, by=c("date_dep", "date_coll", "rhodo_acer", "stream"))
mergecfs2 <- merge(mergecf2, summ_k_shred_yr2, by=c("date_dep", "date_coll", "rhodo_acer", "stream"))
mergecfss2 <- merge(mergecfs2, summ_k_shred_new_yr2, by=c("date_dep","date_coll", "rhodo_acer", "stream"))
lb_si_yr2_dep <- merge(mergecfss2, deployments_yr2, by=c("date_dep","date_coll"))
```


Make YR1 and YR2 LB + phys/chem dfs
```{r} 
#YR1
merge_lb_temp <- merge(lb_si_yr1_dep, dep_temp_si_yr1, by=c("date_dep", "date_coll", "stream", "deployment"))
merge_lb_temp_dis <- merge(merge_lb_temp, dep_discharge_si_yr1, by=c("date_dep", "date_coll", "stream", "deployment"))
all_si_yr1_lb_phys_chem <- merge(merge_lb_temp_dis, dep_nutrients_si_yr1, by=c("date_dep", "date_coll", "stream", "deployment"))

#YR2
merge_lb_temp2 <- merge(lb_si_yr2_dep, dep_temp_si_yr2, by=c("date_dep","date_coll", "stream", "deployment"))
merge_lb_temp_dis2 <- merge(merge_lb_temp2, dep_discharge_si_yr2, by=c("date_dep","date_coll", "stream", "deployment"))
all_si_yr2_lb_phys_chem <- merge(merge_lb_temp_dis2, dep_nutrients_si_yr2, by=c("date_dep","date_coll", "stream", "deployment"))

#write csvs for both years separately:
write.csv(all_si_yr1_lb_phys_chem, "all_si_yr1_lb_phys_chem_1Feb24.csv")
write.csv(all_si_yr2_lb_phys_chem, "all_si_yr2_lb_phys_chem_1Feb24.csv")
```


Make 1 big df with both years
```{r}
all_si_lb_phys_chem_yr1_yr2 <- rbind(all_si_yr1_lb_phys_chem, all_si_yr2_lb_phys_chem)

#write a csv for all the data
write.csv(all_si_lb_phys_chem_yr1_yr2, "all_si_lb_phys_chem_yr1_yr2_1Feb24.csv")
```




